The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-10-07 manuscript/manuscript.tex
update before sharing to TT and JS

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest. In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited. To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic. Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}. This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}. {\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, see Section~\ref{sec:compare_sample}.}

@@

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling provided by this work are preformed through a common procedure for spectral model fits. This approach first correct the spectra for galactic extinction and shift to the rest-frame. The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting. The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

@@

We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data. For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples. The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex. {\bf Note that the B10 only provide the galaxy single V-band luminosity. In \citet{Ding2017b}, the galaxy R-band luminosity are derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04). It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample. In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the sample stellar template. Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

{\bf The values for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2). The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}

@@

{\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector. In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for the gradient in the light distribution. Then, we subtract the globe sky background light to obtain the clear image. To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative. Finally, we extract postage stamp of the AGN image and PSF image to carry out the modeling process, see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}

@@

We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts. We measure the effective radius (\Reff), \sersic\ index, and host-to-total flux ratio and describe each of these in the following section. We recognize that these measurements are weighted by the eight top-ranked PSFs. The limited number of top-ranked PSFs may underestimate actual uncertainties. To gauge how the number of top-ranked PSF affects our results, we compare results when also using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are consistent. For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector. This is against the intuition that it is the PSFs who locates closer to the AGN that have better performance which} highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.

@@

From our image decomposition, we detect the {\bf host galaxy in all cases at a distinguished level, expect one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}. \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases. While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, which indicates the fueling mechanism of AGNs may not be from major mergers for our sample. This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass. In the following subsections, we describe the properties of our ensemble of type-1 AGN host galaxies.

@@

The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}. Based on the sample redshift and the cosmological model, we calculate their physical scale in kpc unit. We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound. The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc). Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge. Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex). 
{\bf Seven systems have low effective radius \Reff$<0\farcs18$ that is within 3 pixels; we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$). In particular, the}
inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero. This means the size inference of these three systems should really be considered an upper limit, rather than a measurement. However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistent result of our re-fitting test and} the small scatter in the host flux ($<10\%$).

@@

For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.  We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides {\bf the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}). {\bf To minimize the uncertainty associated with these corrections, we adopt these two templates correspondingly to interpolate to the rest-frame R band which is very close to the observed wavelengths}. We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.

@@

To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and \citet{H+R04}. In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor. We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution. {\bf We also note the limitations of the local sample we current adopted. For instance, the morphological features like strong bars in B10 were not considered in the decomposition, which might affect the inference of the bulge/disk properties. Also, the HR04 sample does not use color information to estimate the \smass of their sample, rather than use Jeans modeling. These issues have been addressed in the discussions in~\citet{Kormendy13} in detail. Even so, we adopt the B10 and HR04 as our comparison local sample given the following reasons. In this study, we aim to make the differential measurement as function of redshift. With this goal in mind, the consistency between the local and distant sample is crucial in terms of measurement procedure. This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s. galaxy stellar masses, bulge v.s. total and \mbh\ by single epoch v.s. reverberation v.s. dynamical.

@@

For the local sample by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)). This is beyond the comparison medium, i.e., bulge v.s. disk, of ours. Moreover, with a more manageable model, our inference gets ride of the overfitting issue. In spite of this, when adopting the \citet{Bentz2018} as local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
 }

@@

{\bf We summarize several limitations of this work. First, due to limited data qualities, we model the host proper as a single \sersic\ profile. The multi-components feature (e.g., disk$+$bulge) did not appear in the residual map, showing the multi-components information is overwhelmed by the noise level. 
Second, we adopt the common stellar templates to derive the host luminosity and stellar mass for overall sample, which introduces some uncertainty in the inference of the host properties. Even so, the uncertainty in the scaling relations is still dominated by the single epoch black hole mass estimates (see Section~\ref{sec:sysm_err} for detail). Third, for several AGN systems, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as upper limit. However, the inference of their host luminosities and stellar masses are still reliable, given our re-fitting test using different lower limit boundary and the low scatter of the host flux inference (see Section~\ref{sec:result-hosts}, second paragraph). Last, in the literature, there are several different sample could be choose as local anchor to the high-$z$ sample, which could changes the inference of the evolution value. In this work, we adopted the most similar local sample to those at high-$z$. We discussed the different anchors in detail and test to infer the evolution different anchors; all the inference show the positive evolution  (see Section~\ref{sec:local_sys}).}

>>>>

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest. In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited. To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic. Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}. This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}. {\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift from the literature, and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, as shown in Section~\ref{sec:compare_sample}.}

@@

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling provided by this work are preformed through a common procedure for spectral model fits. This approach first corrects the spectra for galactic extinction and shift to the rest-frame. The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting. The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

@@

We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data. For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples. The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex. {\bf Note that the B10 only provides the galaxy single V-band luminosity. In \citet{Ding2017b}, the galaxy R-band luminosity is derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04). It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample. In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the same stellar template. Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

{\bf The values for the all the \mbh-\lhost\ comparison samples are listed in \citet{Ding2017b} (Table~1 and Table~2 therein). The \mbh-\smass\ comparison samples are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}

@@

{\bf Having obtained the \hst\ image, we remove the background light, which could come from both the sky and the detector. In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for the gradient in the light distribution. Then, we subtract the globe sky background light to obtain a clear image. To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative. Finally, we extract the postage stamp of the AGN image and PSF image to carry out the modeling process; see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}

@@

We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts. We measure the effective radius (\Reff), \sersic\ index, and host-to-total flux ratio and describe each of these in the following section. We recognize that these measurements are weighted by the eight top-ranked PSFs. The limited number of top-ranked PSFs may underestimate actual uncertainties. To gauge how the number of top-ranked PSF affects our results, we compare results when also using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are consistent. For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector. This is against the intuition that it is the PSF who locates closer to the AGN that has a better performance, which} highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.

@@

From our image decomposition, we detect the {\bf host galaxy in all cases at a distinguished level, except one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}. \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases. While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, which indicates the fueling mechanism of AGNs may not be from major mergers for our sample. This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass. In the following subsections, we describe the properties of our ensemble of type-1 AGN host galaxies.

@@

The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}. Based on the sample redshift and the cosmological model, we calculate their physical scale in kpc unit. We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound. The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc). Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge. Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex). 
{\bf Seven systems have low effective radius \Reff$<0\farcs18$ that is within 3 pixels; we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$). In particular, the}
inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero. This means the size inference of these three systems should really be considered an upper limit, rather than a measurement. However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistency of the re-fitting results and} the small scatter in the host flux ($<10\%$).

@@

For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.  We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} {\bf provide the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}). {\bf To minimize the uncertainty associated with these corrections, we adopt these two templates correspondingly to interpolate to the rest-frame R band which is very close to the observed wavelengths}. We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.

@@

To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and \citet{H+R04}. In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor. We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution. {\bf We also note the limitations of the local sample we current adopted. For instance, the morphological features like strong bars in B10 were not considered in the decomposition, which might affect the inference of the bulge/disk properties. Also, the HR04 sample does not use color information to estimate the \smass of their sample, rather than use Jeans modeling. These issues have been addressed in the discussions in~\citet{Kormendy13} in detail. Even so, we adopt the B10 and HR04 as our comparison local sample, given the following reasons. In this study, we aim to make the differential measurement as a function of redshift. With this goal in mind, the consistency between the local and distant samples is crucial in terms of the measurement procedure. This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s. galaxy stellar masses, bulge v.s. total and \mbh\ by single epoch v.s. reverberation v.s. dynamical.

@@

For the local sample by \citet{Bentz2018}, with a different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)). This is beyond the comparison medium, i.e., bulge v.s. disk, of ours. Moreover, with a more manageable model, our inference gets ride of the overfitting issue. In spite of this, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
 }

@@

{\bf We summarize several limitations of this work. First, due to limited data qualities, we model the host proper as a single \sersic\ profile. The multi-components feature (e.g., disk$+$bulge) did not appear in the residual map, showing the multi-components information is overwhelmed by the noise level. 
Second, we adopt the universal stellar templates to derive the host luminosity and stellar mass for the overall sample, which introduces some uncertainty in the inference of the host properties. Even so, the uncertainty in the scaling relations is still dominated by the single epoch black hole mass estimates (see Section~\ref{sec:sysm_err} for detail). Third, for several AGN systems, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as the upper limit. However, the inference of their host luminosities and stellar masses are still reliable, given our re-fitting test using different lower limit boundary and the low scatter of the host flux inference (see Section~\ref{sec:result-hosts}, second paragraph). Last, in the literature, there are several different samples that could be chosen as the local anchor to the high-$z$ sample, which could change the inference of the evolution value. In this work, we adopted the most similar local sample to those at high-$z$. We discussed the different anchors in detail and test to infer the evolution trend using different anchors; all the inference show the positive evolution  (see Section~\ref{sec:local_sys}).}
